EvoSwarm: A Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-08-21 draft.tex
Explain out Bastion

Because all these instances run in a private subnet, we also
run a Bastion instance in a public subnet, from where we send the
% what is a Bastion instance? - JJ
commands to execute the experiments
and later collected the results. We connected to this instance through a {\texttt ssh} session from 
our personal workstation. This is a {\texttt R5AD Large} instance, selected with 75GiB of storage, needed for
keeping the logs, and more memory (16GiB) for processing the logs in memory. The details these EC2 instances 
and their cost at the time of writing are shown in Table \ref{tab:ec2}.

@@

In the prior section, we describe an option for an EvoSwarm deployment that can be used by 
the public to create reproductive research in the cloud, in this section we are
using the same framework to learn if the proposed solution can efficiently
improve the scalability and performance of population-based optimization
algorithms. % If you want to prove it *improves*, you need to provide a baseline. 
            %What will be your baseline? You need to specify anyway 
            %in which way it really improves - JJ
            % The baseline is a single population GA or PSO? - M
% For instance. But I was actually looking for another word that does not imply a comparison - JJ
Hence, in the following sections, we verify the following questions:

@@

Section~\ref{sec:exp1} is devoted to answering the first question, and Section~\ref{sec:exp2} to the second.
Next, we describe the general experimental setup to both experiments.

@@

Next, we show the parameters for each algorithm, with Table \ref{tab:GAparams} for
the GA and Table \ref{tab:PSOparams} for the PSO. We obtained these parameters
following the same method as in a previous work \cite{garcia2017benchmarking}.
To obtain the parameters, we tested first on the Rastrigin separable function
with five dimensions. After about fifteen experiments, the most challenging
targets were achieved for this particular function. We tested again with
functions one to three, and after obtaining favorable results, the PSO and GA
algorithm parameters were set. In the GA, we randomly set the mutation and
crossover probabilities to have more heterogeneous workers; 
in these parameters, the range of values is specified. We did not change these parameters during the 
experiments, and only the number of populations, population size and number of generations were
provided as parameters. This strategy has been applied successfully for increasing 
the performance of multi-population algorithms without requiring the setting 
of initial parameters \cite{garcia2014randomized}.

>>>>

Because all these instances run in a private subnet, we also
run a Bastion instance, that is, a specially protected network node, in a public subnet, from where we send the
commands to execute the experiments
and later collected the results. We connected to this instance through a {\texttt ssh} session from 
our personal workstation. This is a {\texttt R5AD Large} instance, selected with 75GiB of storage, needed for
keeping the logs, and more memory (16GiB) for processing the logs in memory. The details these EC2 instances 
and their cost at the time of writing are shown in Table \ref{tab:ec2}.

@@

In the previous section, we have described an option for an EvoSwarm deployment that can be used by 
the public to create reproductive research in the cloud; in this section we are
using the same framework to learn if the proposed solution can efficiently
improve the scalability and performance of population-based optimization
algorithms. 
Hence, in the following sections, we provide answers to the following questions:

@@

Section~\ref{sec:exp1} is devoted to answering the first question, and Section~\ref{sec:exp2} to the second.
Next, we describe the general experimental setup designed to answer
both questions.

@@

Next, we show the parameters for each algorithm, with Table \ref{tab:GAparams} for
the GA and Table \ref{tab:PSOparams} for the PSO. We obtained these parameters
following the same method as in a previous work \cite{garcia2017benchmarking}.
To obtain the parameters, we tested first on the Rastrigin separable function
with five dimensions. After about fifteen experiments, the most challenging
targets were achieved for this particular function. We tested again with
functions one to three, and after obtaining favorable results, the PSO and GA
algorithm parameters were set. In the GA, we randomly set the mutation and
crossover probabilities to have more heterogeneous workers;
for these parameters, the range of values is specified. We did not change these parameters during the 
experiments, and only the number of populations, population size and number of generations were
provided as parameters. This strategy has been applied successfully for increasing 
the performance of multi-population algorithms without requiring the setting 
of initial parameters \cite{garcia2014randomized}.
